Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-16 paper_knowledge.tex
Fixed biblio issues between Akin and I

\item \emph{Location according to an agent}: The predicate
\concept{isLocatedAt} represents spatial locations between agents and objects.
For example we say ``it is on my right, on your left, ...'' These type of direction commands are studied
in the literature in the context of language grounding (\eg \cite{OKeefe1999,Matuszek10}). We compute these
spatial locations by dividing the space around the referent (an agent) into $n$
regions based on arbitrary angle values relative to the referent orientation.
For example, for $n = 4$ we would have the space divided into \emph{front,
left, right} and \emph{back}. Additionally, two proximity values, \emph{near}
and \emph{far}, may also be considered. The number of regions and proximity
values can be chosen depending on the context where the interaction takes
place.

\item \emph{Location according to an object}: We can also refer to object
locations with respect to other objects in the environment, such as \emph{above,
next to, in}, etc. These types of relations are widely studied in language
grounding (\eg \cite{Regier01} presented different models to define the
\emph{above} relation; \cite{Kelleher09} presented two computational models of topological and projective spatial prepositions; \cite{Blisard05} employed contour points of segmented objects to determine \emph{front, behind, left,right} relations). In this work we use similar models based on the
bounding boxes and center of mass of the objects to define three main relations
(Figure~\ref{fig::sprelation}):

>>>>

\item \emph{Location according to an agent}: The predicate
\concept{isLocatedAt} represents spatial locations between agents and objects.
For example we say ``it is on my right, on your left, ...'' These type of direction commands are studied
in the literature in the context of language grounding (\eg \cite{O'Keefe1999,Matuszek2010}). We compute these
spatial locations by dividing the space around the referent (an agent) into $n$
regions based on arbitrary angle values relative to the referent orientation.
For example, for $n = 4$ we would have the space divided into \emph{front,
left, right} and \emph{back}. Additionally, two proximity values, \emph{near}
and \emph{far}, may also be considered. The number of regions and proximity
values can be chosen depending on the context where the interaction takes
place.

\item \emph{Location according to an object}: We can also refer to object
locations with respect to other objects in the environment, such as \emph{above,
next to, in}, etc. These types of relations are widely studied in language
grounding (\eg \cite{Regier2001} presented different models to define the
\emph{above} relation; \cite{Kelleher2009} presented two computational models of topological and projective spatial prepositions; \cite{Blisard2005} employed contour points of segmented objects to determine \emph{front, behind, left,right} relations). In this work we use similar models based on the
bounding boxes and center of mass of the objects to define three main relations
(Figure~\ref{fig::sprelation}):
